%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeWorkSubheading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{graphicx}




\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}
%\textbf{   UserID/email: abrar.nadib@gmail.com}
\begin{center}

    \textbf{\scshape \begin{huge} Khandaker Abrar Nadib \end{huge}} \\ \vspace{1pt}
    \small Email: \href{mailto:abrar.nadib@gmail.com}{\textcolor{blue}{abrar.nadib@gmail.com}} $|$ Github:  \href{https://github.com/AbrarNad}{\textcolor{blue}{AbrarNad}} $|$LinkedIn: \href{https://www.linkedin.com/in/abrar-nadib/}{\textcolor{blue}{abrar-nadib}} $|$ 
    Web: \href{https://abrarnad.github.io/}{\textcolor{blue}{abrarnadib.github.io}}
\end{center}


%-----------EDUCATION-----------
  \section{Research Interests}
  % {Social Computing, Privacy and Security HCI, Health HCI, HCI/design, Network and Systems Security, Intrusion Detection, Malware Detection}
  {My research interest is at the intersection of Social Computing, Human-Computer Interaction (HCI), and Privacy and Security. Specifically, I am interested in
conducting research focusing on understanding and improving user experiences in digital environments.}

  \section{Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{\href{https://ieeexplore.ieee.org/abstract/document/10090133}{{\textcolor{blue}{Interaction Based Credibility Analysis of News on Facebook Using Machine Learning Methodologies}}}} \emph{}}{}
          \resumeItemListStart
            \resumeItem{Published in \href{https://www.sitis-conference.org/2022/}{\textcolor{blue}{16th International Conference on Signal Image Technology \& Internet based Systems (IEEE SITIS-2022)}}.}
            \resumeItem{\textbf{Method:} Predictive Modeling Study; \textbf{Analysis:} Exploratory Data Analysis, Machine Learning.}
          \resumeItemListEnd        
    
    \resumeSubHeadingListEnd
    
  \section{Research Experience}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {News Credibility Analysis on Facebook using User Interactions}{2021 - 2022}
      {Supervisors: \href{https://cse.buet.ac.bd/faculty_list/detail/sadia}{\textcolor{blue}{Dr. Sadia Sharmin}} (BUET) }{}
       \resumeItemListStart
       \resumeItem{The goal was to propose a more efficient solution to determine news authenticity than existing methods.}
       \resumeItem{We developed a method of detecting fake news using interaction metrics on Facebook.}
       \resumeItem{Employed Machine Learning methodologies to classify public Facebook posts based on authenticity.}
       \resumeItem{The proposed method outperforms existing content-based and NLP-based solutions and is also language-independent.}
       \resumeItem{\textbf{Tech}: scikit-learn, pandas, matplotlib.}
       % \resumeItem{A \href{https://ieeexplore.ieee.org/abstract/document/10090133}{\textcolor{blue}{Paper}} was published in SITIS2022 conference. }
        % \resumeItem{Paper titled- \textbf{\href{https://ieeexplore.ieee.org/abstract/document/10090133}{{\textcolor{blue}{Interaction Based Credibility Analysis of News on Facebook Using Machine Learning Methodologies}}}} published in \href{https://www.sitis-conference.org/2022/}{\textcolor{blue}{SITIS2022} conference}.}
      
    \resumeItemListEnd
    
    
    
    \resumeSubHeadingListEnd
    
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Bangladesh University of Engineering and Technology (BUET)}{Dhaka}
      {Bachelor of Science in Computer Science and Engineering}{Feb 2017 --  May,2022}
      \resumeItemListStart
        \resumeItem{\textbf{CGPA: 3.50/4.00}  (Last two semesters: \textbf{3.82})}
         \resumeItem{\textbf{Major CGPA: 3.68/4.00}} 
        
      \resumeItemListEnd
   
      
  \resumeSubHeadingListEnd

\section{Standardized Test Scores}
  \resumeSubHeadingListStart
    \resumeSubheading
      {TOEFL}{}
      {Speaking: 29, Reading: 29, Listening: 28, Writing: 28}{\textbf{114}}
    \resumeSubheading
      {GRE}{}
      {Quant: 162, Verbal: 153, AWA: 4.5}{\textbf{319.5}}
      

  \resumeSubHeadingListEnd

\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeWorkSubheading
        {Software Engineer}{May 2022 -- Present}
        {\href{https://www.optimizely.com/}{\textcolor{blue}{Optimizely}}, Dhaka}{}
        {\textit{Digital Asset Management (DAM)}}{November 2022 -- Present}
        \resumeItemListStart
            \resumeItem{Currently working in the Digital Asset Management (similar to Google Drive) team.}
            \resumeItem{Implemented Brand Template feature, which lets users create a Template for their brand and define Placeholders that other collaborators can edit. I also implemented Download, Export, Cloning, and Task integration features for Brand Templates.}
            \resumeItem{DAM Collections are a group of user-defined Assets, including Asset folders. I implemented Searching, Filtering, and Navigation within DAM Collection folders.}
            \resumeItem{Implemented various asset-specific features like meta information, asset relations, and bulk operations, which enhanced user ability to handle assets.}
            \resumeItem{Implemented breadcrumbs in the DAM Library to make the navigation more fluid for the users.}
            \resumeItem{Implemented various user activity tracking for analytics to gain useful insights.}
            \resumeItem{Made improvements to several backend and UI components in terms of accessibility, performance, and code quality.}
            \resumeItem{Upgraded and integrated GPT-3.5-turbo model for AI content generation.}

            \resumeItem{Handled user roles and privileges for various features.}
            \resumeItem{\textbf{Technologies:} Python, Flask, JavaScript, TypeScript, React.js, MySQL, MongoDB, Alembic, Celery, Elasticsearch}
        \resumeItemListEnd
        \resumeSubSubheading
            {Asset Renditions (AR)}{May 2022 -- October 2022}
            \resumeItemListStart
                \resumeItem{Worked on implementing and maintaining a feature Asset Rendition. This feature allows users to pre-define “Rendition types”, using which whenever users upload a new asset, new “Renditions” of that asset are automatically generated in the background. Example use-case: a user may define two image rendition types- 1. Facebook- 1080*720 crop and Instagram-  720*720 crop. Then whenever the user uploads an image asset, two cropped images will automatically be generated with the given specifications. }
                \resumeItem{Implemented logging schemes by combining multiple services to enable users and developers to diagnose and debug errors.}
                \resumeItem{Built three services to generate asset renditions using the given specifications including image and video generators.}
                \resumeItem{Implemented stateless generators to scale horizontally and integrated asynchronous messaging for decoupling and scaling, for efficiency.}
                \resumeItem{Integrated the Rendition Service with the local development environment for developers.}
                
                \resumeItem{\textbf{Technologies:} Python, FastAPI, MySQL, PostgreSQL, Docker, Kubernetes, Message Queue}
            \resumeItemListEnd
  \resumeSubHeadingListEnd
 

%-----------Academic Projects-----------
\section{Projects}
\resumeSubHeadingListStart
   
       
     \resumeProjectHeading
          {\textbf{\href{https://github.com/AbrarNad/online-art-gallery}{\textcolor{blue}{Online Art Gallery}}} $|$ \emph{Library: React.js, Node.js, Express.js, Mongoose, Database MongoDB }}{2021}
          \resumeItemListStart
            \resumeItem{Designed an e-commerce platform for an Art Gallery.}
        
          \resumeItemListEnd
          \resumeItemListStart
            \resumeItem{ Virtual exhibitions simulated using virtual rooms.}
        
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{\href{https://github.com/AbrarNad/Advanced-Encryption-Standard-AES-}{\textcolor{blue}{AES (Advanced Encryption Standard)}}} $|$ \emph{Language: Python, Libraries: numpy}}{2021}
          \resumeItemListStart
            \resumeItem{Encryption and Decryption algorithm for 128-bit key size implemented
using Python and numpy.}
            
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{\href{https://github.com/AbrarNad/Ray-Tracing}{\textcolor{blue}{Rendering scenes using Ray Tracing}}} $|$ \emph{Language: C, Libraries: OpenGL}}{2022}
          \resumeItemListStart
            \resumeItem{An interactive environment designed in C using OpenGL.}
            
          \resumeItemListEnd
          \resumeItemListStart
            \resumeItem{Lighting for the environment implemented using the Phong Reflection Model}
            
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{\href{https://github.com/AbrarNad/Compiler-for-a-subset-of-C-language}{\textcolor{blue}{Compiler for a Subset of C Language}}} $|$ \emph{Language: C Libraries: Flex, Bison, 8086}}{2020}
          \resumeItemListStart
            \resumeItem{Compiler with parser written in C.}
            
          \resumeItemListEnd
          \resumeItemListStart
            \resumeItem{ Compiles to 8086 machine code.}
            
          \resumeItemListEnd
    

    \resumeProjectHeading
          {\textbf{\href{https://github.com/AbrarNad/Live-Cricket-Scoreboard}{\textcolor{blue}{Live Cricket Scoreboard}}} $|$ \emph{Libraries: JavaFX, Scenebuilder}}{2020}
          \resumeItemListStart
            \resumeItem{A headless app that displays live scores in tabular format.}
            
          \resumeItemListEnd
          \resumeItemListStart
            \resumeItem{Basic files used for storage.}
            
          \resumeItemListEnd
          
        
    \resumeProjectHeading
          {\textbf{\href{https://github.com/meherafrozsworna/online_diagostics_and_consultant_center}{\textcolor{blue}{Backend of an E-commerce Platform}}} $|$ \emph{Language: PHP, Database: PostgreSQL}}{2021}
          \resumeItemListStart
            \resumeItem{Designed the backend of a buy-sell platform.}
            
          \resumeItemListEnd
          \resumeItemListStart
            \resumeItem{ Showcased complex database
queries.}
            
          \resumeItemListEnd
  
    
    
    
     
    \resumeSubHeadingListEnd

      
%--------------Awards-----------
% \section{Awards and Honors}
%   \resumeSubHeadingListStart
%    \resumeSubheading
%     {Optimizely SPOT Award for October and July}{2023}
%     {Nominated by teammates and manager.}{}
%      \resumeItemListStart
%             \resumeItem{\textbf{October}-Awarded for being a team player and positive feedback.}
%             \resumeItem{\textbf{July}- Awarded for tackling challenges head-on and inspiring team growth.}
%         \resumeItemListEnd
    % \resumeSubheading
    % {Optimizely SPOT Award}{July 2023}
    % {Nominated by teammates and manager.}{}
    %  \resumeItemListStart
    %         \resumeItem{Awarded for tackling challenges head-on and inspiring team growth.}
    %     \resumeItemListEnd
    
    % \resumeSubHeadingListEnd
\section{Awards and Honors}
  \resumeSubHeadingListStart
   \resumeSubheading
    {Optimizely SPOT Award}{October 2023}
    {Nominated by teammates and manager.}{}
     \resumeItemListStart
            \resumeItem{Awarded in recognition of excellent performance and contribution.}
        \resumeItemListEnd
    \resumeSubheading
    {Optimizely SPOT Award}{July 2023}
    {Nominated by teammates and manager.}{}
     \resumeItemListStart
            \resumeItem{Awarded in recognition of resolving challenging problems and performance.}
        \resumeItemListEnd
    \resumeSubheading
        {Board Merit Scholarship- HSC}{2016}
        {Education board scholarship}{}
        \resumeItemListStart
            \resumeItem{Ranked 6th(male) in Dhaka board.}
        \resumeItemListEnd
    \resumeSubheading
        {Board Merit Scholarship- SSC}{2014}
        {Education board scholarship}{}

    \resumeSubHeadingListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Research Methods}{: Data Scraping, Surveying, Interviewing} \\
     \textbf{Languages}{: JavaScript, Python, Java, C/C++, SQL, PL/SQL} \\
     \textbf{Database}{: MySQL, Oracle, MongoDB, PostgreSQL}\\
     \textbf{Frameworks}{:  Flask, React.js, Node.JS, Typescript, FastAPI, BootStrap } \\
     \textbf{Tools/Software}{: Git, TensorFlow, Docker, PyCharm, IntelliJ, CodeBlocks, Visual Studio Code, Oracle SQL Developer, Jupyter Notebook, Wireshark} \\
     \textbf{Libraries}{: Pandas, NumPy, Keras, Matplotlib, OpenCV, OpenGL}\\
     % \textbf{Scripting}{: Bash, TCL}\\
     % \textbf{OS}{: Linux, Windows}\\
     \textbf{Scripting/Markup/Serialization}{: Bash, TCL, dLateX, YAML, HTML, JSON};\\
     
    }}
 \end{itemize}



%-----------Volunteering exp-----------
\section{Volunteering and Leadership Experiences}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vice President}{December 2021- May 2022}
      {BUET Computer Club}{}
\resumeItemListStart
      \resumeItem{In charge of organizing and running university events under the club's banner.}
    \resumeItemListEnd
      \resumeSubheading
      {Vice President}{February 2021- April 2022}
      {BUET Dance Club}{}
\resumeItemListStart
      \resumeItem{In charge of organizing events and workshops on campus.}
    \resumeItemListEnd
      

  \resumeSubHeadingListEnd
  
% \section{Standardized Test Scores}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {TOEFL}{}
%       {Speaking: 29, Reading: 29, Listening: 28, Writing: 28}{114}
%     \resumeSubheading
%       {GRE}{}
%       {Quant: 162, Verbal: 153, AWA: 4.5}{319.5}
      

%   \resumeSubHeadingListEnd

\section{References}
  % \setlength\multicolsep{0pt}
  % \begin{multicols}{2}
\href{https://cse.buet.ac.bd/faculty_list/detail/sadia}{\textcolor{blue}{Dr. Sadia Sharmin}},Associate Professor\\ 
\href{https://cse.buet.ac.bd/}{\textcolor{blue}{Department of CSE}}, \href{https://www.buet.ac.bd}{\textcolor{blue}{BUET}}\\
\textbf{Contact: }+880 1817108555\\ \href{mailto:sadiasharmin.ss@gmail.com}{\textcolor{blue}{sadiasharmin.ss@gmail.com}}\\
% \columnbreak
% \href{https://cse.buet.ac.bd/faculty_list/detail/rezwana}{\textcolor{blue}{Dr. Rezwana Reaz}},Assistant Professor\\ 
% \href{https://cse.buet.ac.bd/}{\textcolor{blue}{Department of CSE}}, \href{https://www.buet.ac.bd}{\textcolor{blue}{BUET}}\\
% \textbf{Contact: }+88 01713225520\\ \href{mailto:rimpi0505042@gmail.com}{\textcolor{blue}{rimpi0505042@gmail.com}}\\

% \end{multicols}

%-------------------------------------------
\end{document}
